Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Add the GLAD/EDGI retro gender graph

```{r GLAD/EDGI gender prepan histogram}

GLAD.prepan %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI Cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants")

@@

>>>>

```{r GLAD/EDGI gender prepan}

GLAD.prepan %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants")

@@

###Retrospective

```{r NBR gender prepan}

GLAD.retro %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI retro cohort",
       subtitle = paste("N =", dim(GLAD.retro)[1]),
       x = "",
       y = "N participants")

```{r}
